evidence of adaptation-independent time-warp spike timing noise correlations in cortical networks

### 2020-08-18 manuscript.tex
Lunch

However, short-timescale noise correlations are suggestive of a short-timescale fluctuating state, which covaries neuronal responses and would thus explain a proportion of neural variability. If downstream neurons were also modulated by the same population-wide short-timescale fluctuating state, then downstream `decoder' neurons could respond in a state-dependent manner.
When the fluctuating state has a value on a single trial, a response comes from a \textit{state-conditioned} stimulus-response distribution, which would occupy a smaller region of response distribution space than the region sampled over multiple trials (Fig. 1c). State-dependent decoding therefore offers an improved coding capacity.

This paper aims to precisely characterise shared short-timescale trial-to-trial spike-timing response variability as a step towards inferring the dimensionality of shared short-timescale trial-to-trial state fluctuations (Fig. 1a). This is complicated by changes to neural responses caused by longer-timescale processes, which are therefore controlled for in this paper. This offers a novel prediction of the encoding capacity under a state-dependent coding regime.

>>>>

However, short-timescale noise correlations are suggestive of a short-timescale fluctuating state, which covaries neuronal responses. If downstream neurons were also modulated by the same short-timescale fluctuating state, then downstream `decoder' neurons could respond in a state-dependent manner.
When the fluctuating state has a value on a single trial, a response comes from a \textit{state-conditioned} stimulus-response distribution, which would occupy a smaller region of response distribution space than the region sampled over multiple trials (Fig. 1c). State-dependent decoding would therefore offer an improved coding capacity.

This paper aims to precisely characterise shared short-timescale trial-to-trial spike-timing noise correlations as a step towards inferring the dimensionality of shared short-timescale trial-to-trial state fluctuations (Fig. 1a). If the state fluctuations were low dimensional across a population, then it is more likely that decoding neurons within or outside the population would be modulated by the same fluctuations, and could therefore respond with improved coding capacity in a state-dependent manner.
Characterisation of noise correlations is complicated by changes to neural responses caused by longer-timescale processes. Such longer-timescale changes are therefore are controlled for in this paper, offering a prediction of encoding capacity under a state-dependent coding regime.
